---
title: "COMPSCIX 415.2 Homework 1"
author: "Maithili C. Pabitwar"
date: "6/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

My Github repository for my assignments can be found at this URL: https://github.com/mpabitwar/compscix-415-2-assignments

```{r load_packages, warning=FALSE, message=FALSE}
library(mdsr)
library(tidyverse)
data("WorldCities")
```
QUESTION 1: How many observations and variables are there in this data set? What are some of the variable names?                      
1) There are 23,018 observations and 10 variables in this dataset.  
2) Here are some of the variable names: code, name, latitude, longitude, country, countryRegion, population, regionCode, region, etc.

```{r}
glimpse("WorldCities")
WorldCities <- head(WorldCities, 200)
country_col <- WorldCities$country
unique(country_col)
```
QUESTION 2: There is a column called region in the data set. Can you extract this and show only the unique values?
```{r}
WorldRegion <- WorldCities
region_col <- WorldCities$region
unique(region_col)
```
---
Extract data tidy way
```{r} country_col <- select(WorldCities, country)
country_col <- WorldCities %>% select(country)
WorldCities %>% select(region) %>% head(5)```
---

QUESTION 3: Can you extract and show the unique entries from the country column in WorldCities using one line of code and two %>% operators? The output will look like this:
```{r}
WorldCities %>% select(country) %>% unique()
```
---
Visualize it
```{r}WorldCities %>% ggplot(aes(x = population)) + 
  geom_histogram()
```
---
QUESTION 4: Make one more histogram of the population and add a new x-label, a new y-label, a new title (use ggtitle('my title')), and change the theme of the plot using theme_bw().
```{r}
WorldCities %>% ggplot(aes(x = population)) + 
geom_histogram() +
xlab('City Population') +
ylab('# Cities') +  
ggtitle('Distribution of City Populations') +
theme_bw()  
```